\large Multi-Robot Probabilistic Mapping and Exploration

### 2018-08-28 Dissertation/Defense/phd_research_20min.tex
shortened version for RR (unclassified & open source prior to RR)

\institute{\footnotesize
{\normalsize Evan Kaufman}\\
\vspace*{0.3cm}
Mechanical and Aerospace Engineering\\George Washington University
}

@@

\begin{frame}
\frametitle{Motivation}
\begin{itemize}
	\item Mobile Robotics
	\begin{itemize}
		\item Environments can be dangerous and uncertain
		\item Robots can replace humans for tasks such as surveillance, search-and-rescue, and cleaning
	\end{itemize}
	\pause
	\item Robotic Capabilities
	\begin{itemize}
		\item Robot must understand their environment by generating a map, referred to as \emph{mapping}
		\item Selecting and performing robotic actions to maximize map information, referred to as \emph{autonomous exploration}, is necessary to optimally explore initially-uncertain environments
		\item Cooperative robots can share information to achieve a collective goal with \emph{multi-vehicle exploration and patrol}
		\item These tasks must be performed in 2D and 3D environments, where computational efficiency is paramount to real-time implementation
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Ray Casting}

\begin{itemize}
	\item Required for 2D and 3D occupancy grid maps
	\item Main idea: use simple geometry to find the distance from the robot sensor to each cell intersected by the measurement ray
\end{itemize}

\begin{figure}[!ht]
    \centering
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{RayCastingIllustration.png}
%        \label{fig:penn_map_total}
    \end{subfigure}
    \hspace*{0.05\columnwidth}
    \begin{subfigure}[t]{0.4\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{RayCastIllustrationReducedMapOnly.png}
%        \label{fig:penn_map_zoom}
    \end{subfigure}
\end{figure}

\begin{frame}
\frametitle{Scan Combination Approaches}

\begin{itemize}
	\item \emph{Ray-By-Ray Update}: given a scan of measurement rays, update the map based on each measurement ray \emph{individually} and \emph{sequentially}
	\begin{itemize}
		\item Benefit: the measurement rays maintain some dependency as they capture the same map
		\item Drawback: the best order for evaluating rays is not necessarily chosen
	\end{itemize}
%	\item Conditional probability:
%	\begin{align*}
%		P(\mathbf{m}_i|X_{1:t}&,Z_{1:t})\nonumber\\&
%		=P((\dots(((\mathbf{m}_i|X_{1:t},Z_{1:t-1})|z_{t,1})|z_{t,2})|\ldots)|z_{t,n_z})
%	\end{align*}
	\item \emph{Synergistic Update}: consider every measurement ray inside a scan \emph{simultaneously} to update all grid cells inside the FOV
	\begin{itemize}
		\item Benefit: synergistic update provides a method where all rays are considered simultaneously
		\item Drawback: required assumption that the measurement rays are independent, though they capture the same map
	\end{itemize}
\end{itemize}

@@

\begin{frame}
	\frametitle{2D Autonomous Exploration: Intel Research Lab}
	\centering{
		\includemedia[
  		width=\textwidth,
  		height=0.8\textwidth,
  		activate=pageopen,
  		addresource=IRL.mp4,
  		flashvars={source=IRL.mp4}
		]{}{VPlayer.swf}
		}
\end{frame}

>>>>

\institute{\footnotesize
{\\
\vspace*{0.3cm}
\normalsize Evan Kaufman}\\
\vspace*{0.3cm}
Robotic Research LLC
\\
\vspace*{0.3cm}
September 5, 2018
}

@@

\begin{frame}
\frametitle{Motivation}
\begin{itemize}
	\item Mobile Robotics
	\begin{itemize}
		\item Robots can replace humans dangerous/uncertain tasks such as surveillance, combat, and search-and-rescue
		\item Key question: when robots explore new spaces, how can they maximize their knowledge about their environment?
	\end{itemize}
	\pause
	\item Robotic Capabilities
	\begin{itemize}
		\item Robot must understand their environment by generating a map, referred to as \emph{mapping}
		\item Selecting and performing robotic actions to maximize map information, referred to as \emph{autonomous exploration}
		\item Cooperative robots can share information to achieve a collective goal with \emph{multi-vehicle exploration and patrol}
		\item These tasks must be performed in 2D and 3D environments, where computational efficiency is paramount to real-time implementation
	\end{itemize}
\end{itemize}
\end{frame}

@@

%\begin{frame}
%\frametitle{Ray Casting}
%
%\begin{itemize}
%	\item Required for 2D and 3D occupancy grid maps
%	\item Main idea: use simple geometry to find the distance from the robot sensor to each cell intersected by the measurement ray
%\end{itemize}
%
%\begin{figure}[!ht]
%    \centering
%    \begin{subfigure}[t]{0.4\columnwidth}
%        \centering
%        \includegraphics[width=\textwidth]{RayCastingIllustration.png}
%%        \label{fig:penn_map_total}
%    \end{subfigure}
%    \hspace*{0.05\columnwidth}
%    \begin{subfigure}[t]{0.4\columnwidth}
%        \centering
%        \includegraphics[width=\textwidth]{RayCastIllustrationReducedMapOnly.png}
%%        \label{fig:penn_map_zoom}
%    \end{subfigure}
%\end{figure}
%
%\end{frame}

%\begin{frame}
%\frametitle{Scan Combination Approaches}
%
%\begin{itemize}
%	\item \emph{Ray-By-Ray Update}: given a scan of measurement rays, update the map based on each measurement ray \emph{individually} and \emph{sequentially}
%	\begin{itemize}
%		\item Benefit: the measurement rays maintain some dependency as they capture the same map
%		\item Drawback: the best order for evaluating rays is not necessarily chosen
%	\end{itemize}
%%	\item Conditional probability:
%%	\begin{align*}
%%		P(\mathbf{m}_i|X_{1:t}&,Z_{1:t})\nonumber\\&
%%		=P((\dots(((\mathbf{m}_i|X_{1:t},Z_{1:t-1})|z_{t,1})|z_{t,2})|\ldots)|z_{t,n_z})
%%	\end{align*}
%	\item \emph{Synergistic Update}: consider every measurement ray inside a scan \emph{simultaneously} to update all grid cells inside the FOV
%	\begin{itemize}
%		\item Benefit: synergistic update provides a method where all rays are considered simultaneously
%		\item Drawback: required assumption that the measurement rays are independent, though they capture the same map
%	\end{itemize}
%\end{itemize}
%
%\end{frame}

@@

%\begin{frame}
%	\frametitle{2D Autonomous Exploration: Intel Research Lab}
%	\centering{
%		\includemedia[
%  		width=\textwidth,
%  		height=0.8\textwidth,
%  		activate=pageopen,
%  		addresource=IRL.mp4,
%  		flashvars={source=IRL.mp4}
%		]{}{VPlayer.swf}
%		}
%\end{frame}
